---
title: "Star Wars Analysis"
bibliography: starwars-references.bib
output: 
  bookdown::html_document2:
    base_format: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{starwrs-analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 5,
  fig.retina = 2
)
```

```{r setup}
library(mysimplecompedium)
library(dplyr)
library(ggplot2)
```

```{r read-external-code}
knitr::read_chunk("my-script.R") 
```


## Introduction
Due to the recently released Star Wars film, "Star Wars: The Rise of Skywalker: Expanded Edition", we will be analyzing the Star Wars data set, which is already loaded into dplyr and has:

```{r data-intro, echo=FALSE} 
``` 


## Analysys
Distribution of height of Star Wars characters:

```{r, starwars-plot, fig.cap = "A density plot of heights."}
ggplot(data = starwars,
       mapping = aes(x = height))+
  geom_density()+
  theme_bw()
```

We can see in Figure \@ref(fig:starwars-plot) a density plot of all the different heights of Star Wars characters.


IThere is an upcoming book that will adapt the events of the film, with some extended and unseen scences [@starwars9book].

## References cited
